---
title: "BFAS_SF_ptwo"
author: "Christopher"
date: "`r Sys.Date()`"
output: 
  html_document: 
    toc: yes
    toc_depth: 3
    highlight: textmate
    theme: yeti
    fig_height: 7.5
    keep_md: yes
---

```{r set opts, include = F}
knitr::opts_chunk$set(fig.width=12, fig.height=8, echo=FALSE, warning=FALSE, message=FALSE)
```

```{r setup, warnings=FALSE, comment=F}


library(tidyverse, quietly = TRUE)
library(magrittr, quietly = TRUE)
library(sjmisc, quietly = TRUE)
library(corrr, quietly = TRUE)
library(knitr, quietly = TRUE)
library(kableExtra, quietly = TRUE)
library(reactable, quietly = TRUE)

```

# Reanalysis of the Study 2 Raw Data

```{r data, message=FALSE, warning=FALSE}

s2_possible_attn <- read_csv("Study2Data_manip.csv") %>%
  select(ResponseId, easy_attn, easy_attn2, Chk1_1:Less,ABL2, total_na)

s2_bfas <- read_csv("Study2Data_manip.csv") %>% 
  select(ResponseId, Vol_1:Plt_10, Ind_1:Asrt_10, Ord_1:Ord_10,Enth_1:Asrt_10, Intel_1:Open_10) %>% select(-HAP_1, -HLTH)
                                                                
s2_aux_vars <- read_csv("Study2Data_manip.csv") %>% 
  select(ResponseId,Age, Race, Edu, GEN, HHincome, ABLE:Less, ABL2, POP, HOT, HLTH, 
         starts_with("GRP"), starts_with("IMP")) %>%
  rename(imp_fam = IMP_1, imp_frnd = IMP_2, imp_fun =  IMP_3, imp_poli =IMP_4, imp_wrk = IMP_5, imp_relig = IMP_6)

```

## Workflow

-   [x] **screen -- see screening section**

-   [x] **compute competence**

-   [x] ~~**What's up with Sandia?**~~ **Psychometrics, alt forms. (sandia axed)**

-   [x] **note the chosen SF items:**\~\~ ***listed in the code chunk***

-   [x] **score the BFAS and CAS or LATS or whatever our SF gets to be named**\~\~

-   [x] **score relative imp, grips, ~~sandia~~, auxvars**

-   [ ] **Correlation matrices with:**

    -   [x] Big and Little

    -   [x] Importance and Little

    -   [x] Other stuff (GRIPS and small scales) and Little

    -   [x] basic reliability stuff

    -   [ ] present better

-   [ ] **compare with past results**

-   [ ] **anything I'm missing?**

-   [ ] **table focusing on difference (full minus short) correlations with aux vars**

-   [ ] **upload what we have so far to osf, etc**

::: {#Top}
Compare it to the old correlations, though.
:::

\#\#Scoring Aux

```{r ABLEaux}

##ability
s2_aux_vars %>% sjmisc::set_na(., More, na = -99) ->  s2_aux_vars
s2_aux_vars$Ability <- rowSums(s2_aux_vars[, c(8:10)], na.rm = TRUE)
s2_aux_vars$SR_Competence <- s2_aux_vars$Ability +  s2_aux_vars$ABL2
s2_aux_vars <- s2_aux_vars %>% row_means(., contains("GRP"), 
                         n = 4, append = TRUE, var = "Risk_Pref")

##dumb rev code fxn
domain_rev_code <- function(x, na.rm = FALSE){
  (5-x)
}


## domain relative importance
domains_df <- s2_aux_vars  %>% select(imp_fam:imp_relig) %>% mutate_all(., domain_rev_code)
domains_df <- domains_df %>% row_sums(., contains("imp"), 
                         n = 2, append = TRUE, var = "Imp_Tot")
domains_df <- domains_df %>% rowwise() %>% mutate(., rel_fam = imp_fam/Imp_Tot) %>%
  mutate(., rel_frnd = imp_frnd/Imp_Tot) %>% mutate(., rel_fun = imp_fun/Imp_Tot) %>% 
  mutate(., rel_poli = imp_poli/Imp_Tot) %>% mutate(., rel_wrk = imp_wrk/Imp_Tot) %>% 
  mutate(., rel_relig = imp_relig/Imp_Tot)

```

## Scoring Notes:

domains are available as single items or relative importance (domain importance rating/sum of them), but nnote that there are multiple ways this is scored.

Able correlates with Able 2 at `r round(cor(s2_aux_vars$Ability, s2_aux_vars$ABL2), digits=2)`

```{r ablplot, echo=TRUE, fig.height=4, fig.width=4}
scatter.smooth(s2_aux_vars$Ability, s2_aux_vars$ABL2)
## domain relative importance -- just a check.

```

Self-reported ability items work well together for an index. 

## Reversing BFAS, Scoring Full BFAS

```{r afunctionandreversed}

## These are the reversed items in the full BFAS 

rev_bfas <- c("Vol_2", "Vol_4", "Vol_6", "Vol_8", "With_1", "With_3", "With_5", "With_8", "Comp_1", "Comp_4", "Comp_6", "Comp_7", "Comp_9", "Plt_2", "Plt_4", "Plt_7", "Plt_8", "Plt_9", "Plt_10", "Ind_2", "Ind_3", "Ind_4", "Ind_6", "Ind_9", "Ind_10", "Ord_1", "Ord_5", "Ord_7", "Ord_8", "Enth_2", "Enth_3", "Enth_4", "Enth_6", "Enth_7", "Asrt_3", "Asrt_5", "Asrt_8", "Asrt_10", "Intel_2", "Intel_5", "Intel_6", "Intel_9", "Open_5", "Open_8", "Open_9", "Open_10")

s2_bfas_rec <- s2_bfas  %>% modify_at(., .at = rev_bfas, ~6-.x)
head(cbind(s2_bfas$Open_10, s2_bfas_rec$Open_10))
## note -- I thought there were missing oppenness chunks?


#rm(s2_bfas)

## SCORING 

s2_bfas_rec <- s2_bfas_rec %>% row_means(., contains("Vol"), 
                         n = 5, append = TRUE, var = "Volatility")
s2_bfas_rec <- s2_bfas_rec %>% row_means(., contains("With"), 
                         n = 5, append = TRUE, var = "Withdrawal")
s2_bfas_rec <- s2_bfas_rec %>% row_means(., contains("Comp"), 
                         n = 5, append = TRUE, var = "Compassion")
s2_bfas_rec <- s2_bfas_rec %>% row_means(., contains("Plt"), 
                         n = 5, append = TRUE, var = "Politeness")
s2_bfas_rec <- s2_bfas_rec %>% row_means(., contains("Ind"), 
                         n = 5, append = TRUE, var = "Industriousness")
s2_bfas_rec <- s2_bfas_rec %>% row_means(., contains("Ord"), 
                         n = 5, append = TRUE, var = "Orderliness")
s2_bfas_rec <- s2_bfas_rec %>% row_means(., contains("Enth"), 
                         n = 5, append = TRUE, var = "Enthusiasm")
s2_bfas_rec <- s2_bfas_rec %>% row_means(., contains("Asrt"), 
                         n = 5, append = TRUE, var = "Assitiveness")
s2_bfas_rec <- s2_bfas_rec %>% row_means(., contains("Intel"), 
                         n = 5, append = TRUE, var = "Intellect")
s2_bfas_rec <- s2_bfas_rec %>% row_means(., contains("Open"), 
                         n = 5, append = TRUE, var = "Openness")

```

## Scoring our LATS

```{r LATS}
LATS <- c("Vol_1", "Vol_3", "Vol_9", "Vol_10", "With_2", "With_5", "With_6", "With_10", "Comp_2", "Comp_3", "Comp_8", "Comp_10", "Plt_2", "Plt_6", "Plt_7", "Plt_8", "Ind_2", "Ind_3", "Ind_4", "Ind_10", "Ord_2", "Ord_3", "Ord_6", "Ord_7", "Enth_2", "Enth_3", "Enth_4", "Enth_7", "Asrt_1", "Asrt_2", "Asrt_5", "Asrt_6", "Intel_1", "Intel_2", "Intel_3", "Intel_6", "Open_1", "Open_3", "Open_9", "Open_10")

## because apparently this is what dplyr needs
s2_LATS <- s2_bfas_rec %>% select(all_of(LATS))

## SCORING 

s2_LATS <- s2_LATS %>% row_means(., contains("Vol"), 
                                 n = 2, append = TRUE, var = "Volatility_L") %>% 
  row_means(., contains("With"), n = 2, append = TRUE, var = "Withdrawal_L") %>% 
  row_means(., contains("Comp"), n = 2, append = TRUE, var = "Compassion_L") %>% 
  row_means(., contains("Plt"),  n = 2, append = TRUE, var = "Politeness_L") %>% 
  row_means(., contains("Ind"),n = 2,append = TRUE,var = "Industriousness_L") %>% 
  row_means(., contains("Ord"), n = 2, append = TRUE, var = "Orderliness_L") %>% 
  row_means(., contains("Enth"), n = 2, append = TRUE, var = "Enthusiasm_L") %>% 
  row_means(., contains("Asrt"), n = 2, append = TRUE, var = "Assitiveness_L") %>% 
  row_means(., contains("Intel"), n = 2, append = TRUE, var = "Intellect_L") %>% 
  row_means(., contains("Open"), n = 2, append = TRUE, var = "Openness_L")

```

## Original conception of screening (pass/fail) rules

TOTAL BLANKS \> 40% (count \~ 72 for actual questions); fail (1) vs pass (0)

attn checks are: easy_attn & easy_attn2

select the center square (0), any other (1)

ABLE asks: are you more or less competent than average (more, average, less), if more (How much more competent? with an option including "less") and vice versa.

-   only 1 person failed to be consistent, but that's a (0) and a (1) for everyone else.\
    We would also expect their answer to be consistent with Abl2, but we can skip it if I'm being picky\
    total of fail/pass attn checks should be ?

A look at all quality indexes, with all irrelevant block selections to be removed

*Out of 5 possible checks, 40ish failed 1 or 2. I think the 2/5 rule works fine here, even though we had not been using it initially.*

### Filtering based on this more stringent requirement.

From the raw data, I have N= 333 with N = 305 fit for analyses. This is in contrast to 321 in the manuscript. The difference mainly comes from using all indices (one of which no one failed).

```{r cleaning it up}

##cleaning it up

s2_possible_attn$box_attn <- if_else(s2_possible_attn$Chk1_1 == "On",  0, 1)
s2_possible_attn$ableM_attn <- if_else(s2_possible_attn$More == -99,  1, 0)
s2_possible_attn$ableL_attn <- if_else(s2_possible_attn$Less == -99,  1, 0)
s2_possible_attn$na_perc_attn <- if_else(s2_possible_attn$total_na >36, 1, 0)
s2_possible_attn <- s2_possible_attn[, -c(5:12)]
s2_possible_attn %>% select(easy_attn2, box_attn:na_perc_attn) -> s2_likely_attn
rmarkdown::paged_table(s2_likely_attn[1:50,])
attn_fail_tot <-  as.matrix(rowSums(s2_likely_attn, na.rm = TRUE)) 
table(as.factor(attn_fail_tot)) %>% as.data.frame() %>% 
  knitr::kable(., "html", col.names = c("# failed", "count"))

## cleaning it up end
```

```{r bind_filter}

## creating our frame of useable scores (not included are demographics)
##### 
scores <- bind_cols(s2_bfas_rec[,102:111], s2_LATS[, 41:50], s2_aux_vars[,c(2,4, 6, 11:13,29, 30)], domains_df[ , -7],  as.data.frame(attn_fail_tot))
scores <- scores %>% filter(V1 == 0) %>% select(-V1)
```

```{r alphas}
lats_alphas <- tibble(.rows = 10, row.names = names(s2_bfas_rec[,102:111]))
lats_alphas$alphas <- rep(0, 10)
s2_LATS  %>%  select(Vol_1:Vol_10) %>% 
  psych::alpha() -> y;y$total[1] -> lats_alphas[1,"alphas"]
s2_LATS  %>%  select(With_2:With_10) %>%
  psych::alpha() -> y;y$total[1] -> lats_alphas[2,"alphas"]
s2_LATS  %>%  select(Comp_2:Comp_10) %>% 
  psych::alpha() -> y;y$total[1] -> lats_alphas[3,"alphas"] 
s2_LATS  %>%  select(Plt_2:Plt_8) %>%
  psych::alpha() -> y;y$total[1] -> lats_alphas[4,"alphas"]
s2_LATS  %>%  select(Ind_2:Ind_10) %>% 
  psych::alpha() -> y;y$total[1] -> lats_alphas[5,"alphas"]
s2_LATS  %>%  select(Ord_2:Ord_7) %>% 
  psych::alpha() -> y;y$total[1] -> lats_alphas[6,"alphas"] 
s2_LATS  %>%  select(Enth_2:Enth_7) %>% 
  psych::alpha() -> y;y$total[1] -> lats_alphas[7,"alphas"]
s2_LATS  %>%  select(Asrt_1:Asrt_6) %>% 
  psych::alpha() -> y;y$total[1] -> lats_alphas[8,"alphas"]
s2_LATS  %>%  select(Intel_1:Intel_6) %>% 
  psych::alpha()-> y;y$total[1] -> lats_alphas[9,"alphas"]
s2_LATS  %>%  select(Open_1:Open_10) %>% 
  psych::alpha() -> y;y$total[1] -> lats_alphas[10,"alphas"]

full_alphas <- tibble(.rows = 10, row.names = names(s2_bfas_rec[,102:111]))
full_alphas$alphas <- rep(0, 10)
s2_bfas_rec  %>%  select(Vol_1:Vol_10) %>% 
  psych::alpha() -> y;y$total[1] -> full_alphas[1,"alphas"]
s2_bfas_rec  %>%  select(With_1:With_10) %>%
  psych::alpha() -> y;y$total[1] -> full_alphas[2,"alphas"]
s2_bfas_rec  %>%  select(Comp_1:Comp_10) %>% 
  psych::alpha() -> y;y$total[1] -> full_alphas[3,"alphas"] 
s2_bfas_rec  %>%  select(Plt_1:Plt_10) %>%
  psych::alpha() -> y;y$total[1] -> full_alphas[4,"alphas"]
s2_bfas_rec  %>%  select(Ind_1:Ind_10) %>% 
  psych::alpha() -> y;y$total[1] -> full_alphas[5,"alphas"]
s2_bfas_rec  %>%  select(Ord_1:Ord_10) %>% 
  psych::alpha() -> y;y$total[1] -> full_alphas[6,"alphas"] 
s2_bfas_rec  %>%  select(Enth_1:Enth_10) %>% 
  psych::alpha() -> y;y$total[1] -> full_alphas[7,"alphas"]
s2_bfas_rec  %>%  select(Asrt_1:Asrt_10) %>% 
  psych::alpha() -> y;y$total[1] -> full_alphas[8,"alphas"]
s2_bfas_rec  %>%  select(Intel_1:Intel_10) %>% 
  psych::alpha()-> y;y$total[1] -> full_alphas[9,"alphas"]
s2_bfas_rec  %>%  select(Open_1:Open_10) %>% 
  psych::alpha() -> y;y$total[1] -> full_alphas[10,"alphas"]
s2_bfas_rec %>% select(Volatility:Openness) %>% corrr::correlate() %>% shave -> BFAS_cormat 
s2_LATS %>% select(Volatility_L:Openness_L) %>% corrr::correlate() %>% shave -> LATS_cormat 
scores %>% dplyr::select(Volatility_L:Openness_L)  -> LATS_scores 
scores %>% dplyr::select(Volatility:Openness) -> BFAS_scores
scores %>% dplyr::select(Volatility:Openness_L) -> LATS_BFAS_scores

```

```{r alphas2}
lats_alphas %>% kbl(caption = "Little BFAS with alphas") %>%
  kable_styling(full_width = F, bootstrap_options = "condensed", html_font = 'Fira Mono' )
full_alphas %>% kbl(caption = "Little BFAS with alphas") %>%
  kable_styling(full_width = F, bootstrap_options = "condensed", html_font = 'Fira Mono' )
```

## Correlations Follow:

### Full form with Little Form

**I don't like these style options, so let's figure out better table formats**

```{r bfascormat}

## correlation matrix
scores %>% select(Volatility:Openness_L) %>% correlate(., diagonal = 1) %>% round_num(., digits = 2) -> dom_asp_cormat
 

## correlation matrix
dom_asp_cormat  %>%
  kbl(caption = "BFAS with Little BFAS") %>%
  kable_styling(full_width = F, bootstrap_options = "condensed", html_font = 'Fira Mono') %>% 
  scroll_box(width = "750px", height = "100%")
                                                             
  
```

### LATS with absolute importance

```{r rel}

## build
scores %>% select(Volatility_L:Openness_L,rel_fam:rel_relig) %>%  
  correlate() %>% round_num(., digits = 2) -> life_1_cor
scores %>% select(Volatility_L:Openness_L,imp_fam:imp_relig) %>%
  correlate() %>% round_num(., digits = 2)  -> life_2_cor

## correlation matrix

life_1_cor  %>%
  kbl(caption = "Abs Importance  with Little BFAS") %>%
  kable_styling(full_width = F, bootstrap_options = "condensed", html_font = 'Fira Mono') %>%   scroll_box(width = "750px", height = "100%")

```

### LATS with relative importance

```{r abs}

## correlation matrix

life_2_cor  %>%
  kbl(caption = "Little BFAS with Absolute Importance") %>%
  kable_styling(full_width = F, bootstrap_options = "condensed", html_font = 'Fira Mono', ) %>% 
  scroll_box(width = "750px", height = "100%")
```

### LATS with GRiPs and the rest

```{r others}
## correlation matrix

scores %>% select(Volatility_L:Openness_L, Age:SR_Competence) %>% correlate() %>% 
        sjmisc::round_num(., digits = 2) -> remains_cor
remains_cor  %>%
  kbl(caption = "Little BFAS with The Other Stuff") %>%
  kable_styling(full_width = F, bootstrap_options = "condensed", html_font = 'Fira Mono', ) %>% 
  scroll_box(width = "750px", height = "100%")
```

## Code Appendix

------------------------------------------------------------------------

```{r ref.label=knitr::all_labels(), echo=TRUE, eval=FALSE}

```

------------------------------------------------------------------------
